### 2023-04-11 chapter2/chapter2_supporting.tex
Replaced source with range in feature table

\begin{landscape}
\footnotesize
\begin{longtable}{|l|l|l|l|l|l|}
\caption{\textbf{Features and their definitions.}}
\label{stable:features}
% Start first head
\hline
\textbf{Feature ID}    & \textbf{Feature name}                                                            & \textbf{Group name}                                                & \textbf{Source} & \textbf{Description}                                                                                                             & \begin{tabular}[c]{@{}l@{}}\textbf{Changes from}\\\textbf{Zarin \textit{et al.}}~\cite{Zarin2019}\end{tabular}
\endfirsthead

% Start head
\multicolumn{6}{l}
{\textbf{\tablename\ \thetable} (continued)} \\
\hline
\textbf{Feature ID}    & \textbf{Feature name}                                                            & \textbf{Group name}                                                & \textbf{Source} & \textbf{Description}                                                                                                             & \begin{tabular}[c]{@{}l@{}}\textbf{Changes from}\\\textbf{Zarin \textit{et al.}~\cite{Zarin2019}}\end{tabular}
\endhead

@@

fraction\_S            & S fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        &                 &                                                                                                                                  &                                                                                                \\

@@

fraction\_P            & P fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        &                 &                                                                                                                                  &                                                                                                \\

@@

fraction\_T            & T fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        &                 &                                                                                                                                  &                                                                                                \\

@@

fraction\_A            & A fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        &                 &                                                                                                                                  &                                                                                                \\

@@

fraction\_H            & H fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        &                 &                                                                                                                                  &                                                                                                \\

@@

fraction\_Q            & Q fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        &                 &                                                                                                                                  &                                                                                                \\

@@

fraction\_N            & N fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        &                 &                                                                                                                                  &                                                                                                \\

@@

fraction\_G            & G fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        &                 &                                                                                                                                  &                                                                                                \\

@@

FCR                    & \begin{tabular}[c]{@{}l@{}}fraction charged\\residues\end{tabular}               & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         &                 & basic residue fraction + acidic residue fraction                                                                                 &                                                                                                \\

@@

NCPR                   & \begin{tabular}[c]{@{}l@{}}net charge\\per residue\end{tabular}                  & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         &                 & basic residue fraction - acidic residue fraction                                                                                 &                                                                                                \\

@@

net\_charge            & net charge                                                                       & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         &                 & \#{[}RK] - \#{[}DE]                                                                                                              &                                                                                                \\

@@

net\_charge\_P         & \begin{tabular}[c]{@{}l@{}}net charge with\\phosphorylation\end{tabular}         & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         &                 & \begin{tabular}[c]{@{}l@{}}net charge including phosphorylation of [ST]P\\consensus sites with -1.5 charge per site\end{tabular} &                                                                                                \\

@@

kappa                  & kappa                                                                            & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         & localcider      & \begin{tabular}[c]{@{}l@{}}measure of separation between positively\\and negatively charged residues\end{tabular}                &                                                                                                \\

@@

omega                  & omega                                                                            & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         & localcider      & \begin{tabular}[c]{@{}l@{}}measure of separation between charged\\residues or prolines and all other residues\end{tabular}       &                                                                                                \\

@@

SCD                    & \begin{tabular}[c]{@{}l@{}}sequence charge\\decoration\end{tabular}              & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         & localcider      & \begin{tabular}[c]{@{}l@{}}measure of separation between positively\\and negatively charged residues\end{tabular}                &                                                                                                \\

@@

RK\_ratio              & R/K ratio                                                                        & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         &                 & \begin{tabular}[c]{@{}l@{}}adjusted ratio of arginine to\\lysine residues: (\#R + 1)/(\#K + 1)\end{tabular}                      &                                                                                                \\

@@

ED\_ratio              & E/D ratio                                                                        & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         &                 & \begin{tabular}[c]{@{}l@{}}adjusted ratio of glutamic acid to\\aspartic acid residues: (\#E + 1)/(\#D + 1)\end{tabular}          &                                                                                                \\

@@

fraction\_acidic       & \begin{tabular}[c]{@{}l@{}}acidic\\residue fraction~\end{tabular}                & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} &                 &                                                                                                                                  &                                                                                                \\

@@

fraction\_basic        & \begin{tabular}[c]{@{}l@{}}basic\\residue fraction\end{tabular}                  & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} &                 &                                                                                                                                  &                                                                                                \\

@@

fraction\_aliphatic    & \begin{tabular}[c]{@{}l@{}}aliphatic\\residue fraction\end{tabular}              & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} &                 &                                                                                                                                  &                                                                                                \\

@@

fraction\_polar        & \begin{tabular}[c]{@{}l@{}}polar\\residue fraction\end{tabular}                  & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} &                 &                                                                                                                                  & removed glycine                                                                                \\

@@

fraction\_chainexp     & \begin{tabular}[c]{@{}l@{}}chain-expanding\\residue fraction\end{tabular}        & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} &                 &                                                                                                                                  &                                                                                                \\

@@

fraction\_aromatic     & \begin{tabular}[c]{@{}l@{}}aromatic\\residue fraction\end{tabular}               & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} &                 &                                                                                                                                  &                                                                                                \\

@@

fraction\_disorder     & \begin{tabular}[c]{@{}l@{}}disorder-promoting\\residue fraction\end{tabular}     & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} &                 &                                                                                                                                  &                                                                                                \\

@@

radius\_gyration       & radius of gyration                                                               & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} &                 & number of residues to the 0.6 power                                                                                              & \begin{tabular}[c]{@{}l@{}}substituted\\for length\end{tabular}                                \\

@@

hydropathy             & hydropathy                                                                       & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} & localcider      & normalized Kyte-Doolittle scale                                                                                                  &                                                                                                \\

@@

isopoint               & isoelectric point                                                                & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} & isoelectric     & pH where charge of peptide is neutral                                                                                            &                                                                                                \\

@@

PPII\_propensity       & PPII propensity                                                                  & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} & localcider      & \begin{tabular}[c]{@{}l@{}}propensity for proline to form\\left-handed helices\end{tabular}                                      &                                                                                                \\

@@

repeat\_Q              & Q repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive Q                                                                                                 &                                                                                                \\

@@

repeat\_N              & N repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive N                                                                                                 &                                                                                                \\

@@

repeat\_S              & S repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive S                                                                                                 &                                                                                                \\

@@

repeat\_G              & G repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consectuive G                                                                                                 &                                                                                                \\

@@

repeat\_E              & E repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive E                                                                                                 &                                                                                                \\

@@

repeat\_D              & D repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive D                                                                                                 &                                                                                                \\

@@

repeat\_K              & K repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive K                                                                                                 &                                                                                                \\

@@

repeat\_R              & R repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive R                                                                                                 &                                                                                                \\

@@

repeat\_P              & P repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive P                                                                                                 &                                                                                                \\

@@

repeat\_QN             & {[}QN] repeat fraction                                                           & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive [QN]                                                                                              &                                                                                                \\

@@

repeat\_RG             & {[}RG] repeat fraction                                                           & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive [RG]                                                                                              &                                                                                                \\

@@

repeat\_FG             & {[}FG] repeat fraction                                                           & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive [FG]                                                                                              &                                                                                                \\

@@

repeat\_SG             & {[}SG] repeat fraction                                                           & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive [SG]                                                                                              &                                                                                                \\

@@

repeat\_SR             & {[}SR] repeat fraction                                                           & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive [SR]                                                                                              &                                                                                                \\

@@

repeat\_AP             & {[}KAP] repeat fraction                                                          & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive [KAP]                                                                                             &                                                                                                \\

@@

repeat\_TS             & {[}PTS] repeat fraction                                                          & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    &                 & fraction 2 or more consecutive [PTS]                                                                                             &                                                                                                \\

@@

wf\_complexity         & \begin{tabular}[c]{@{}l@{}}Wootton-Federhen\\sequence complexity\end{tabular}    & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & localcider      & \begin{tabular}[c]{@{}l@{}}complexity based on SEG algorithm:\\blob length=IDR length, step size=1\end{tabular}                  &                                                                                                \\

@@

CLV\_Separin\_Metazoa  & separase cleavage motif                                                          & motifs                                                             &                 &                                                                                                                                  & \begin{tabular}[c]{@{}l@{}}Metazoa motif\\instead of fungi\end{tabular}                        \\

@@

DEG\_APCC\_KENBOX\_2   & \begin{tabular}[c]{@{}l@{}}APCC-binding\\destruction motif\end{tabular}          & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

DEG\_APCC\_TPR\_1      & APCC-TPR-docking motif                                                           & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

DOC\_CKS1\_1           & Cks1 ligand                                                                      & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

DOC\_MAPK\_DCC\_7      & MAPK docking motif                                                               & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

DOC\_MAPK\_gen\_1      & MAPK docking motif                                                               & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

DOC\_MAPK\_HePTP\_8    & MAPK docking motif                                                               & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

DOC\_PP1\_RVXF\_1      & PP1-docking motif RVXF                                                           & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

DOC\_PP2B\_PxIxI\_1    & \begin{tabular}[c]{@{}l@{}}calcineurin (PP2B)-\\docking motif PxIxI\end{tabular} & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

LIG\_APCC\_Cbox\_1     & \begin{tabular}[c]{@{}l@{}}APC/C\_Apc2-docking\\motif\end{tabular}               & motifs                                                             &                 &                                                                                                                                  & \begin{tabular}[c]{@{}l@{}}Metazoa motif\\instead of fungi\end{tabular}                        \\

@@

LIG\_AP\_GAE\_1        & \begin{tabular}[c]{@{}l@{}}gamma-adaptin ear\\interaction motif\end{tabular}     & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

LIG\_CaM\_IQ\_9        & \begin{tabular}[c]{@{}l@{}}helical calmodulin\\binding motif\end{tabular}        & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

LIG\_EH\_1             & EH ligand                                                                        & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

LIG\_eIF4E\_1          & eIF4E binding motif                                                              & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

LIG\_GLEBS\_BUB3\_1    & GLEBS motif                                                                      & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

LIG\_LIR\_Gen\_1       & \begin{tabular}[c]{@{}l@{}}Atg8 protein\\family ligands\end{tabular}             & motifs                                                             &                 &                                                                                                                                  & \begin{tabular}[c]{@{}l@{}}same ELM entry,\\but updated regex\end{tabular}                     \\

@@

LIG\_PCNA\_PIPBox\_1   & PCNA binding PIP box                                                             & motifs                                                             &                 &                                                                                                                                  & \begin{tabular}[c]{@{}l@{}}same ELM entry,\\but updated regex\end{tabular}                     \\

@@

LIG\_SUMO\_SIM\_par\_1 & \begin{tabular}[c]{@{}l@{}}SUMO interaction\\site\end{tabular}                   & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

MOD\_CDK\_SPxK\_1      & \begin{tabular}[c]{@{}l@{}}CDK phosphorylation\\site\end{tabular}                & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

MOD\_LATS\_1           & \begin{tabular}[c]{@{}l@{}}LATS kinase\\phosphorylation motif\end{tabular}       & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

MOD\_SUMO\_for\_1      & sumoylation site                                                                 & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

TRG\_ER\_FFAT\_1       & FFAT motif                                                                       & motifs                                                             &                 &                                                                                                                                  & \begin{tabular}[c]{@{}l@{}}same ELM entry,\\but updated regex\end{tabular}                     \\

@@

TRG\_Golgi\_diPhe\_1   & ER export signals                                                                & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

TRG\_NLS\_MonoExtN\_4  & \begin{tabular}[c]{@{}l@{}}classical nuclear\\localization signals\end{tabular}  & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

@@

DOC\_PRO               & proline rich motif                                                               & motifs                                                             &                 &                                                                                                                                  &                                                                                                \\

>>>>

\begin{landscape}
\footnotesize
\begin{longtable}{|l|l|l|l|l|l|}
\caption{\textbf{Features and their definitions.}}
\label{stable:features}
% Start first head
\hline
\textbf{Feature ID}    & \textbf{Feature name}                                                            & \textbf{Group name}                                                & \textbf{Range} & \textbf{Description}                                                                                                             & \begin{tabular}[c]{@{}l@{}}\textbf{Changes from}\\\textbf{Zarin \textit{et al.}}~\cite{Zarin2019}\end{tabular}
\endfirsthead

% Start head
\multicolumn{6}{l}
{\textbf{\tablename\ \thetable} (continued)} \\
\hline
\textbf{Feature ID}    & \textbf{Feature name}                                                            & \textbf{Group name}                                                & \textbf{Range} & \textbf{Description}                                                                                                             & \begin{tabular}[c]{@{}l@{}}\textbf{Changes from}\\\textbf{Zarin \textit{et al.}~\cite{Zarin2019}}\end{tabular}
\endhead

@@

fraction\_S            & S fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        & {[}0, 1]                     &                                                                                                                                  &                                                                                                \\

@@

fraction\_P            & P fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        & {[}0, 1]                     &                                                                                                                                  &                                                                                                \\

@@

fraction\_T            & T fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        & {[}0, 1]                     &                                                                                                                                  &                                                                                                \\

@@

fraction\_A            & A fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        & {[}0, 1]                     &                                                                                                                                  &                                                                                                \\

@@

fraction\_H            & H fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        & {[}0, 1]                     &                                                                                                                                  &                                                                                                \\

@@

fraction\_Q            & Q fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        & {[}0, 1]                     &                                                                                                                                  &                                                                                                \\

@@

fraction\_N            & N fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        & {[}0, 1]                     &                                                                                                                                  &                                                                                                \\

@@

fraction\_G            & G fraction                                                                       & \begin{tabular}[c]{@{}l@{}}amino acid\\content\end{tabular}        & {[}0, 1]                     &                                                                                                                                  &                                                                                                \\

@@

FCR                    & \begin{tabular}[c]{@{}l@{}}fraction charged\\residues\end{tabular}               & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         & {[}0, 1]                     & basic residue fraction + acidic residue fraction                                                                                 &                                                                                                \\

@@

NCPR                   & \begin{tabular}[c]{@{}l@{}}net charge\\per residue\end{tabular}                  & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         & {[}-1, 1]                    & basic residue fraction - acidic residue fraction                                                                                 &                                                                                                \\

@@

net\_charge            & net charge                                                                       & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         & ($-\infty$, $\infty$)        & \#{[}RK] - \#{[}DE]                                                                                                              &                                                                                                \\

@@

net\_charge\_P         & \begin{tabular}[c]{@{}l@{}}net charge with\\phosphorylation\end{tabular}         & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         & ($-\infty$, $\infty$)        & \begin{tabular}[c]{@{}l@{}}net charge including phosphorylation of [ST]P\\consensus sites with -1.5 charge per site\end{tabular} &                                                                                                \\

@@

kappa                  & kappa                                                                            & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         & (0, 1]                       & \begin{tabular}[c]{@{}l@{}}measure of separation between positively\\and negatively charged residues\end{tabular}                &                                                                                                \\

@@

omega                  & omega                                                                            & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         & (0, 1]                       & \begin{tabular}[c]{@{}l@{}}measure of separation between charged\\residues or prolines and all other residues\end{tabular}       &                                                                                                \\

@@

SCD                    & \begin{tabular}[c]{@{}l@{}}sequence charge\\decoration\end{tabular}              & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         & ($-\infty$, $\infty$)        & \begin{tabular}[c]{@{}l@{}}measure of separation between positively\\and negatively charged residues\end{tabular}                &                                                                                                \\

@@

RK\_ratio              & R/K ratio                                                                        & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         & (0, $\infty$)                & \begin{tabular}[c]{@{}l@{}}adjusted ratio of arginine to\\lysine residues: (\#R + 1)/(\#K + 1)\end{tabular}                      &                                                                                                \\

@@

ED\_ratio              & E/D ratio                                                                        & \begin{tabular}[c]{@{}l@{}}charge\\properties\end{tabular}         & (0, $\infty$)                & \begin{tabular}[c]{@{}l@{}}adjusted ratio of glutamic acid to\\aspartic acid residues: (\#E + 1)/(\#D + 1)\end{tabular}          &                                                                                                \\

@@

fraction\_acidic       & \begin{tabular}[c]{@{}l@{}}acidic\\residue fraction~\end{tabular}                & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} & {[}0 ,1]                     &                                                                                                                                  &                                                                                                \\

@@

fraction\_basic        & \begin{tabular}[c]{@{}l@{}}basic\\residue fraction\end{tabular}                  & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} & {[}0 ,1]                     &                                                                                                                                  &                                                                                                \\

@@

fraction\_aliphatic    & \begin{tabular}[c]{@{}l@{}}aliphatic\\residue fraction\end{tabular}              & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} & {[}0 ,1]                     &                                                                                                                                  &                                                                                                \\

@@

fraction\_polar        & \begin{tabular}[c]{@{}l@{}}polar\\residue fraction\end{tabular}                  & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} & {[}0 ,1]                     &                                                                                                                                  & removed glycine                                                                                \\

@@

fraction\_chainexp     & \begin{tabular}[c]{@{}l@{}}chain-expanding\\residue fraction\end{tabular}        & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} & {[}0 ,1]                     &                                                                                                                                  &                                                                                                \\

@@

fraction\_aromatic     & \begin{tabular}[c]{@{}l@{}}aromatic\\residue fraction\end{tabular}               & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} & {[}0 ,1]                     &                                                                                                                                  &                                                                                                \\

@@

fraction\_disorder     & \begin{tabular}[c]{@{}l@{}}disorder-promoting\\residue fraction\end{tabular}     & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} & {[}0 ,1]                     &                                                                                                                                  &                                                                                                \\

@@

radius\_gyration       & radius of gyration                                                               & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} & {[}0,~ $\infty$)             & number of residues to the 0.6 power                                                                                              & \begin{tabular}[c]{@{}l@{}}substituted\\for length\end{tabular}                                \\

@@

hydropathy             & hydropathy                                                                       & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} & {[}0 ,1]                     & normalized Kyte-Doolittle scale                                                                                                  &                                                                                                \\

@@

isopoint               & isoelectric point                                                                & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} & ($-\infty$, $\infty$)        & pH where charge of peptide is neutral                                                                                            &                                                                                                \\

@@

PPII\_propensity       & PPII propensity                                                                  & \begin{tabular}[c]{@{}l@{}}physiochemical\\properties\end{tabular} & {[}0, 1]                     & \begin{tabular}[c]{@{}l@{}}propensity for proline to form\\left-handed helices\end{tabular}                                      &                                                                                                \\

@@

repeat\_Q              & Q repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive Q                                                                                                 &                                                                                                \\

@@

repeat\_N              & N repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive N                                                                                                 &                                                                                                \\

@@

repeat\_S              & S repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive S                                                                                                 &                                                                                                \\

@@

repeat\_G              & G repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consectuive G                                                                                                 &                                                                                                \\

@@

repeat\_E              & E repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive E                                                                                                 &                                                                                                \\

@@

repeat\_D              & D repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive D                                                                                                 &                                                                                                \\

@@

repeat\_K              & K repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive K                                                                                                 &                                                                                                \\

@@

repeat\_R              & R repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive R                                                                                                 &                                                                                                \\

@@

repeat\_P              & P repeat fraction                                                                & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive P                                                                                                 &                                                                                                \\

@@

repeat\_QN             & {[}QN] repeat fraction                                                           & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive [QN]                                                                                              &                                                                                                \\

@@

repeat\_RG             & {[}RG] repeat fraction                                                           & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive [RG]                                                                                              &                                                                                                \\

@@

repeat\_FG             & {[}FG] repeat fraction                                                           & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive [FG]                                                                                              &                                                                                                \\

@@

repeat\_SG             & {[}SG] repeat fraction                                                           & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive [SG]                                                                                              &                                                                                                \\

@@

repeat\_SR             & {[}SR] repeat fraction                                                           & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive [SR]                                                                                              &                                                                                                \\

@@

repeat\_AP             & {[}KAP] repeat fraction                                                          & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive [KAP]                                                                                             &                                                                                                \\

@@

repeat\_TS             & {[}PTS] repeat fraction                                                          & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & fraction 2 or more consecutive [PTS]                                                                                             &                                                                                                \\

@@

wf\_complexity         & \begin{tabular}[c]{@{}l@{}}Wootton-Federhen\\sequence complexity\end{tabular}    & \begin{tabular}[c]{@{}l@{}}repeats and\\complexity\end{tabular}    & {[}0, 1]                     & \begin{tabular}[c]{@{}l@{}}complexity based on SEG algorithm:\\blob length=IDR length, step size=1\end{tabular}                  &                                                                                                \\

@@

CLV\_Separin\_Metazoa  & separase cleavage motif                                                          & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  & \begin{tabular}[c]{@{}l@{}}Metazoa motif\\instead of fungi\end{tabular}                        \\

@@

DEG\_APCC\_KENBOX\_2   & \begin{tabular}[c]{@{}l@{}}APCC-binding\\destruction motif\end{tabular}          & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

DEG\_APCC\_TPR\_1      & APCC-TPR-docking motif                                                           & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

DOC\_CKS1\_1           & Cks1 ligand                                                                      & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

DOC\_MAPK\_DCC\_7      & MAPK docking motif                                                               & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

DOC\_MAPK\_gen\_1      & MAPK docking motif                                                               & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

DOC\_MAPK\_HePTP\_8    & MAPK docking motif                                                               & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

DOC\_PP1\_RVXF\_1      & PP1-docking motif RVXF                                                           & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

DOC\_PP2B\_PxIxI\_1    & \begin{tabular}[c]{@{}l@{}}calcineurin (PP2B)-\\docking motif PxIxI\end{tabular} & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

LIG\_APCC\_Cbox\_1     & \begin{tabular}[c]{@{}l@{}}APC/C\_Apc2-docking\\motif\end{tabular}               & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  & \begin{tabular}[c]{@{}l@{}}Metazoa motif\\instead of fungi\end{tabular}                        \\

@@

LIG\_AP\_GAE\_1        & \begin{tabular}[c]{@{}l@{}}gamma-adaptin ear\\interaction motif\end{tabular}     & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

LIG\_CaM\_IQ\_9        & \begin{tabular}[c]{@{}l@{}}helical calmodulin\\binding motif\end{tabular}        & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

LIG\_EH\_1             & EH ligand                                                                        & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

LIG\_eIF4E\_1          & eIF4E binding motif                                                              & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

LIG\_GLEBS\_BUB3\_1    & GLEBS motif                                                                      & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

LIG\_LIR\_Gen\_1       & \begin{tabular}[c]{@{}l@{}}Atg8 protein\\family ligands\end{tabular}             & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  & \begin{tabular}[c]{@{}l@{}}same ELM entry,\\but updated regex\end{tabular}                     \\

@@

LIG\_PCNA\_PIPBox\_1   & PCNA binding PIP box                                                             & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  & \begin{tabular}[c]{@{}l@{}}same ELM entry,\\but updated regex\end{tabular}                     \\

@@

LIG\_SUMO\_SIM\_par\_1 & \begin{tabular}[c]{@{}l@{}}SUMO interaction\\site\end{tabular}                   & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

MOD\_CDK\_SPxK\_1      & \begin{tabular}[c]{@{}l@{}}CDK phosphorylation\\site\end{tabular}                & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

MOD\_LATS\_1           & \begin{tabular}[c]{@{}l@{}}LATS kinase\\phosphorylation motif\end{tabular}       & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

MOD\_SUMO\_for\_1      & sumoylation site                                                                 & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

TRG\_ER\_FFAT\_1       & FFAT motif                                                                       & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  & \begin{tabular}[c]{@{}l@{}}same ELM entry,\\but updated regex\end{tabular}                     \\

@@

TRG\_Golgi\_diPhe\_1   & ER export signals                                                                & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

TRG\_NLS\_MonoExtN\_4  & \begin{tabular}[c]{@{}l@{}}classical nuclear\\localization signals\end{tabular}  & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\

@@

DOC\_PRO               & proline rich motif                                                               & motifs                                                             & {[}0, $\infty$)              &                                                                                                                                  &                                                                                                \\
